State of the Practice for Lattice Boltzmann Method Software

### 2022-04-23 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
reviewed Section 6

For the dependency tools (Table~\ref{tbl_tools}), we observed that most of the
software packages use some sort of build automation tools, most commonly Make.
They all use various technical and domain specific libraries. Technical
libraries include visualization (e.g.,\ Matplotlib, ParaView, Pygame, VTK), data
analysis (e.g.,\ Anaconda, Torch), and message passing libraries (e.g.,\ MPICH,
Open MPI, PyZMQ). Domain specific libraries include research software libraries
(e.g.,\ SciPy).

@@

CI is the process of building and testing software on every push to the code
repository, with pushes done very frequently \citep[p.\ 13]
{HumbleAndFarley2010}, \citep{ShahinEtAl2017, Fowler2006}.  CI consists of the
following elements:
\begin{itemize}
	\item A version control system \citep{Fowler2006}. To be effective, all
	files should be under version control, not just code files.  Anything that
	is needed to build, install and run the software should be under version
	control, including configuration files, build scripts, test harnesses, and
	operating system configurations \citep[p. 19]{HumbleAndFarley2010}.
	Fortunately for the LBM domain, as discussed above, most alive projects
	(73\% of those assessed) use version control.
	\item A fully automated build system \citep{Fowler2006}.  As \citet[p.\
	5]{HumbleAndFarley2010} point out, deploying software manually is an
	anti-pattern.  Fortunately, as discussed above, most LBM projects use build
	automation.
	\item An automated test system \citep{Fowler2006}. Building quality software
	involves creating automated tests at the unit, component, and acceptance
	test level, and executing these tests whenever a change is made to the code,
	its configuration, the environment, or the software stack that it runs on
	\citep[p.\ 83]{HumbleAndFarley2010}. As Table~\ref{artifactspresent} shows
	test cases are in the uncommon category for LBM software artifacts, which
	means that some LBM projects will need to increase their testing automation
	if they wish to pursue CI.  The usual advice for CI is to keep the build and
	test process short \citep[p.\ 60]{HumbleAndFarley2010}. Given that LBM can
	be computationally expensive, the tests run with every check-in may need to
	focus on simple code interface tests, saving larger more complex tests for
	less frequent runs.  A more sophisticated option for when tests create a
	bottleneck for merges is CIVET (Continuous Integration,
	Verification, Enhancement, and Testing), which solves this problem by
	intelligently pinning, cancelling, and if necessary, restarting jobs as
	merges occur, so that two merges are being tested at all times
	\citep{SlaughterEtAl2021}.
	\item An automated system for other tasks, such as code checking,
	documentation building and web-site updating.  These other tasks are not
	essential parts of CI, but they can be incorporated to improve the quality
	of the code and the communication between developers and users. For
	instance, a static analysis (possibly via linters) of the code may find poor
	programming practice or lack of adherence to adopted coding standards.
	\citet{SlaughterEtAl2021} provides another example of an automated task --
	checking that a test specification includes the test's motivation, a test
	description, and a design description for all changes. 
	\item An integration build system to pull everything together.  Every time
	there is a check-in (for instance a pull request), the integration server
	automatically checks out the sources onto the integration machine, starts a
	build, runs tests, and informs the committer of the results. 
\end{itemize}

@@

\begin{itemize}
	\item Headaches associated with a separate integration phase are eliminated
	\citep{Fowler2006}, \citep[p.\ 20]{HumbleAndFarley2010}. If integration of
	the work of different developers, or even separate chunks of work by the
	same developer, is postponed, integration problems are inevitable.  By
	continuously integrating problems are immediately obvious, and the source of
	the problem can be isolated to the small increment that was just committed.
	\item Bugs can be quickly detected and removed \citep{Fowler2006} via
	automated testing.  To improve productivity, defects are best discovered and
	fixed at the point where they are introduced \citep[p.\
	23]{HumbleAndFarley2010}.  Errors are not just found in the code, but also
	in the files and scripts related to configuration management \citep[p.\
	18]{HumbleAndFarley2010}.
	\item Developers are always working on a stable base, since the master
	branch will always be working.  A stable base passes all tests and, if the
	CI system is configured with generators and linters, it will also have current documentation and coding standard compliant code.  A stable base
	improves developer productivity, allowing them to focus on coding, testing
	and documentation.
\end{itemize}

>>>>

For the dependency tools (Table~\ref{tbl_tools}), we observe that most of the
software packages use some sort of build automation tools, most commonly Make.
They all use various technical and domain specific libraries. Technical
libraries include visualization (e.g.,\ Matplotlib, ParaView, Pygame, VTK), data
analysis (e.g.,\ Anaconda, Torch), and message passing libraries (e.g.,\ MPICH,
Open MPI, PyZMQ). Domain specific libraries include research software libraries
(e.g.,\ SciPy).

@@

CI is the process of building and testing software on every push to the code
repository, with pushes done very frequently \citep[p.\ 13]
{HumbleAndFarley2010}, \citep{ShahinEtAl2017, Fowler2006}.  CI consists of the
following elements:
\begin{itemize}
	\item A version control system \citep{Fowler2006}. To be effective, all
	files should be under version control, not just code files.  Anything that
	is needed to build, install and run the software should be under version
	control, including configuration files, build scripts, test harnesses, and
	operating system configurations \citep[p. 19]{HumbleAndFarley2010}.
	Fortunately for the LBM domain, as discussed above, most alive projects
	(73\% of those assessed) use version control.
	\item A fully automated build system \citep{Fowler2006}.  As \citet[p.\
	5]{HumbleAndFarley2010} point out, deploying software manually is an
	anti-pattern.  Fortunately, as discussed above, most LBM projects use build
	automation.
	\item An automated test system \citep{Fowler2006}. Building quality software
	involves creating automated tests at the unit, component, and acceptance
	test level, and executing these tests whenever a change is made to the code,
	its configuration, the environment, or the software stack that it runs on
	\citep[p.\ 83]{HumbleAndFarley2010}. As Table~\ref{artifactspresent} shows,
	test cases are in the uncommon category for LBM software artifacts, which
	means that some LBM projects will need to increase their testing automation
	if they wish to pursue CI.  The usual advice for CI is to keep the build and
	test process short \citep[p.\ 60]{HumbleAndFarley2010}. Given that LBM can
	be computationally expensive, the tests run with every check-in may need to
	focus on simple code interface tests, saving larger more complex tests for
	less frequent runs.  A more sophisticated option for when tests create a
	bottleneck for merges is CIVET (Continuous Integration,
	Verification, Enhancement, and Testing), which solves this problem by
	intelligently pinning, cancelling, and if necessary, restarting jobs as
	merges occur, so that two merges are being tested at all times
	\citep{SlaughterEtAl2021}.
	\item An automated system for other tasks, such as code checking,
	documentation building and web-site updating.  These other tasks are not
	essential parts of CI, but they can be incorporated to improve the quality
	of the code and the communication between developers and users. For
	instance, a static analysis (possibly via linters) of the code may find poor
	programming practice or lack of adherence to adopted coding standards.
	\citet{SlaughterEtAl2021} provides another example of an automated task --
	checking that a test specification includes the test's motivation, a test
	description, and a design description for all changes. 
	\item An integration build system to pull everything together.  Every time
	there is a check-in (for instance a pull request), the integration server
	automatically checks out the sources onto the integration machine, starts a
	build, runs tests, and informs the committer of the results. 
\end{itemize}

@@

\begin{itemize}
	\item Headaches associated with a separate integration phase are eliminated
	\citep{Fowler2006}, \citep[p.\ 20]{HumbleAndFarley2010}. If integration of
	the work of different developers, or even separate chunks of work by the
	same developer, is postponed, integration problems are inevitable.  By
	continuously integrating, problems are immediately obvious and the source of
	the problem can be isolated to the small increment that was just committed.
	\item Bugs can be quickly detected and removed \citep{Fowler2006} via
	automated testing.  To improve productivity, defects are best discovered and
	fixed at the point where they are introduced \citep[p.\
	23]{HumbleAndFarley2010}.  Errors are not just found in the code, but also
	in the files and scripts related to configuration management \citep[p.\
	18]{HumbleAndFarley2010}.
	\item Developers are always working on a stable base, since the master
	branch will always be working.  A stable base passes all tests and, if the
	CI system is configured with generators and linters, it will also have current documentation and coding standard compliant code.  A stable base
	improves developer productivity, allowing them to focus on coding, testing
	and documentation.
\end{itemize}
